\sysfull

### 2017-07-29 paper/background.tex

Task is a programmer (or compiler) defined code that is executed based on consistent set of inputs, i.e. memory fetched from a specified memory location, producing a consistent output stored in a specified (the same or different) memory location. Syntactically, we can treat a task as a continuous sub-section of a large program encapsulated by (i) task specific keywords defining the beginning and the end of a task and (ii) message passing between tasks connected with each other.

@@

Just like Chain~\cite{chain} and Alpaca~\cite{alpaca}, \sys does not support concurrent programming, multi-threading (multi-task sequence) and does not consider priorities and on-demand scheduling. These features are extremely important to consider but go beyond the scope of this work. A comparative description of \sys is given in Table~\ref{table:feature_comparison}.

>>>>

\todo{Please check this is the right way for this section: it reads as it should be in Section 3 describing \sys}{Brandon} Task is a programmer (or compiler) defined code that is executed based on consistent set of inputs, i.e. memory fetched from a specified memory location, producing a consistent output stored in a specified (the same or different) memory location. Syntactically, we can treat a task as a continuous sub-section of a large program encapsulated by (i) task specific keywords defining the beginning and the end of a task and (ii) message passing between tasks connected with each other.

@@

Just like Chain~\cite{chain} and Alpaca~\cite{alpaca}, \sys does not support concurrent programming, multi-threading (multi-task sequence) and does not consider priorities and on-demand scheduling. These features are extremely important to consider but go beyond the scope of this work. A comparative description of \sys is given in Table~\ref{table:feature_comparison}. \todo{Decide if we need such table}{Brandon}
